---
#title: "WebPresence"
#author: "Joseph Doucette"
#date: "10/31/2016"
output: html_document
runtime: shiny
---
```{r setup, include=FALSE}
#=============================================================================
#
#     __                            __           __     __    
#    / /__  _--.  __  __  -,--.  __/ /_ _--.    / /   / /_--.
#   / // / / _ | / / / / / __ | /_  __// _ |   / /.   / // _.|
#  /  '_/ / // // / / / / / | |  / /  / // |  / _ \  / // ___/
# / /\ \ / // // /_/ | / /  / / / /  / //  | / // / / // /_-. 
#/_/ |_| \___/ \___/|//_/  /_/ /_/   \___/|//_ __/ /_/ \___/
#
#
# Name        : MarkerShinyNewIO.Rmd
# Original Author      : Joseph Doucette
# Updated by  : Joseph Doucette
# Created     : 07/11/2016
# Version     : 1.51
# A Part of   : Kountable R Library
# Copyright   : Kountable, Inc
# Description : Rmarkdown Shiny Application for online KYC of users
#             : These were 'extracted' from the Delphi code lib with permission
#
#  Software Copyright (c) 2016 by: kountable, inc.,
#                                  2535 E Southlake Tx, Suite 100
#                                  Southlake, TX 76092
#
#  This software is furnished only under a license and may be used and copied
#  only according to the terms and conditions of such license and with the
#  inclusion of the above copyright notice and this license statement.
#  Neither this software nor any copies thereof may be distributed, provided
#  or made available to any other person - either as source code or as modules
#  in its compiled forms.  The use of this software is intended only for the
#  benefit of valid license holders. No title to the software, the methodology
#  for calculations, the algorithms or any other intellectual property of
#  kountable, Inc is hereby transferred.
#
#============================================================================
source('kApiKYCCallsSource.R')
# source('web_searchSource.R')
source('WebPresence.R')
library(dplyr)
library(DT)
library(shiny)
## get the list of users from the Swagger Api calls  This builds the drop down list
userSearchName <- get.V2UsersList()
# ls.results <- readRDS("/Users/doucetteemail/Documents/KountableFiles/RDevelopment/RMarker/RMarker/data/tbl.zOuput.rds")
```
```{r myHeader, echo=FALSE}
# fluidPage(tags$img(src = "https://cdn.brandisty.com/img?id=5547ab6a2da09beb4c000007&format=jpg", width=400),style="background-color:#033951;")
# fluidPage(tags$img(src = "www/Kountable-White_rgb_1200_266.jpg", width=400),style="background-color:#033951;")
  
```
# Webpresence
```{r main, echo=FALSE}
  fluidPage(
    theme='bootstrap.css',
    fluidRow(
#      h2('KYC Report -Alpha 1.75'), 
      tags$div(tags$h3("Report Date: ", tags$b(strftime(Sys.time(),"%Y-%m-%d %H:%M:%S"), style ="color: #fff"))),
      hr(),
      HTML("<div class='alert alert-info'>",
           "<strong>Heads up!</strong> AML searching defaults to <em>free</em>. WorldCheck searches are fee based, use only at approapriate trade finance stages in the Kountable Certified Entrepreneur qualification system. <a href='http://kountable.com' class='alert-link'>Kountable, Inc.</a>. ","</div>"),
      style="background-color:#2593d1;"),
    fluidRow(column(12, htmlOutput("chooseUUID1")), style="background-color:#2593d1;")
    # "<strong>Heads up!</strong> This is a <em>prototype</em> of the many key KYC applications available to <a href='http://kountable.com' class='alert-link'>Kountable, Inc.</a>. ","</div>"
    )
  
output$chooseUUID1 = renderUI({
  list(
    tags$div(selectInput(inputId = "selectUserId1", label = h4("Select UserId"), choices = userSearchName, selected = '504',
                         selectize = FALSE, width = 450)),
    tags$div(actionButton("goButton1", "Go!",icon("paper-plane"),
                          style="border-color: #2e6da4", width = 100))
    )
  })

selectedUserId <- eventReactive(input$goButton1, {
  print("ntext")
    input$selectUserId1
  })
WebPresence <- eventReactive(input$goButton1, {
                               cat('Calling get.WebPresence for selectedUserId ---> ',selectedUserId(), '\n')
                               
                               withProgress(message = 'getting WebPresence Analytics Data',
                                            detail = 'This may take a while...', 
                                            value = 0, {
                                              for (i in 1:4) {
                                                incProgress(1/4)
                                                Sys.sleep(0.25)}
                                              
                                            get.WebPresence(uuid =  selectedUserId())
                                              })
                               
                                })
# createResultFile <- reactive({
#                                cat('Calling get.createresultfile for selectedUserId ---> ',selectedUserId(), '\n')
#                                
#                                get.createresultfile(urls = WebPresence(), uuid =  selectedUserId())
#                      })

```

## WebPresence Table
***

```{r FrankProfile, echo=FALSE}
DT::dataTableOutput("webPresenceTable")
##frankProfileData()[,c('kActive','kScore','profile','data')]
output$webPresenceTable = DT::renderDataTable({
        DT::datatable( WebPresence()$tbl.urls, class='compact stripe', escape = FALSE, rownames = FALSE,
                                   caption = tags$caption(style = 'caption-side: top; text-align: left;',
                                             tags$div(tags$h3("WebPresence Summary for: ",
                                             tags$b(paste0(WebPresence()$uuid), style = 'color:blue')
                                             ))),
                                   options = list(
                                                 #order = list(list(2, 'desc'), list(4, 'desc')),
                                                  pageLength=nrow(WebPresence()$tbl.urls), # needs to match nrow on the table, currently with 4 addins its 24
                                                  bLengthChange=0, # show/hide records per page dropdown
                                                  bFilter=0,       # global search box on/off
                                                  bInfo=0,         #removes # of reccords filter bottom left
                                                  bPaginate=0      #removes the page select bottom right
                                                  # columnDefs = list(list(width = 50, targets = c(0)),
                                                  #                   list(width = 400, targets = c(1))
                                                  #                   #list(className="dt-center", targets=c(0,1))
                                                  #                   )
                                                  )
        )
      })
